---
title: "exhibit Introduction"
author: "Andy Merlino"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exhibit Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

We want to create pdf and html reports using the `ChainLadder` package reserve projection functions.  Many of the `ChainLadder` functions return complicated objects stored as lists.  The exhibit package grabs the most important data for presentation from these objects and converts it into a matrix or data frame that is easy to understand and easy to display in an html or pdf report.

## Examples

```{r load_packages, message = FALSE}
# load packages
library(ChainLadder)
library(exhibit)
library(xtable)
options(xtable.comment = FALSE)
options(xtable.type = "html")
```

We are going to use the `RAA` object provided by the `ChainLadder` package. `RAA` is an S3 object of class triangle from the `ChainLadder` package.  It looks like a nice triangle when it is printed to the R console. Additionally the results from the MackChainLadder function look nice when printed to the R console:

```{r RAA}
RAA

MackChainLadder(RAA)
```

but if you try to make a table out of the triangle you end up with this

```{r }
out <- xtable(RAA)
print(out,
  format.args = list(big.mark = ",")      
)
```

This is because `ChainLadder` stores more information than is shown in the R console in its classes.  The classes returned from projection methodologies can store a lot of information and can be hard to navigate.  Take a look at the structure of the class returned from the `MackChainLadder()` function:

```{r}
out <- MackChainLadder(RAA)
str(out)
```

`ChainLadder` uses generic functions to print and summarize its classes to the R console.  This is nice if you are only printing your results to the R console, but we want to quickly display the results in an html or pdf report.  To do this we use the `exhibit()` function to grab only the information we want from the respective `ChainLadder` class and return it as a 2-dimensional matrix or data frame.

Here are a few examples:

```{r exhibit_triangle, results = "asis"}
out <- exhibit(RAA)
out <- xtable(out)
print(out,
  format.args = list(big.mark = ",")
)
```

```{r mack, results = "asis"}
RAA_mack <- MackChainLadder(RAA)
RAA_mack_out <- exhibit(RAA_mack)
RAA_mack_out <- xtable(RAA_mack_out,
                  digits = c(0, 0, 2, 0, 0, 0)
                )
print(RAA_mack_out,
  format.args = list(big.mark = ",")     
)
```