---
title: "exhibit Introduction"
author: "Andy Merlino"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exhibit Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

We want to create pdf and html reports using the `ChainLadder` package reserve projection functions.  Many of the `ChainLadder` functions return complicated lists.  The exhibit package grabs the most important data from these lists and converts it into a matrix or data frame that is easy to understand and easy to display in an html or pdf report.

## Examples

```{r load_packages, message = FALSE}
# load packages
library(ChainLadder)
library(exhibit)
library(xtable)
options(xtable.comment = FALSE)
options(xtable.type = "html")
```

We are going to use the `RAA` object provided by the `ChainLadder` package. `RAA` is an S3 object of class triangle from the `ChainLadder` package.  It looks like a nice triangle when it is printed to the R console: 

```{r RAA}
RAA
```

but we want to display the triangle in an Rmarkdown report, not in the R console.

Here are a few examples:

```{r exhibit_triangle, results = "asis"}
out <- exhibit(RAA)
out <- xtable(out)
print(out,
  format.args = list(big.mark = ",")
)
```

```{r mack, results = "asis"}
RAA_mack <- MackChainLadder(RAA)
RAA_mack_out <- exhibit(RAA_mack)
RAA_mack_out <- xtable(RAA_mack_out,
                  digits = c(0, 0, 2, 0, 0, 0)
                )
print(RAA_mack_out,
  format.args = list(big.mark = ",")     
)
```