---
title: "exhibit for the ChainLadder package"
author: "Andy Merlino"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

## Intro

Like many modeling functions in R, the ChainLadder functions for estimating insurance reserves return objects of data structure type list.  These lists contain a lot more information than the user typically needs, and they also often make it difficult for the user to identify what he or she really wants.  The exhibit package grabs the most typically desired data from the lists returned by `ChainLadder` functions and returns it as a matrix or data frame that is easy to understand and easy to display in an html or pdf report.

## Examples

```{r load_packages, message = FALSE}
# load packages
library(ChainLadder)
library(exhibit)
library(knitr)
```

```{r triangles}
RAA
names(RAA)
str(RAA)
colnames(RAA)
rownames(RAA)
```

`RAA` is an example triangle that comes with the `ChainLadder` package.  It looks fine when we print it out like this, but we want to print it out in a html or latex table for a report, rather than printing it as R output.

If we try to run `knitr::kable(RAA)`, `xtable::xtable(RAA)`, or `pander::pander(RAA)` we get an error.  The error is because `ChainLadder` uses generic print functions for most of its classes to make the R output look nice, but the structure of the actual R object can be quite different than what appears when the object is printed.

```{r exhibit_triangle}
kable(exhibit(RAA))
```
